\tool: Revisiting BadUSB with Type-C

### 2021-03-21 WOOT/Files/__latexindent_temp.tex

In this part, we survey related works on USB attack in Section~\ref{subsec:usb_attack}, and USB defence security in Section \ref{subsec:usb_defence}, respectively.

@@

From the hardware perspective, BadUSB attack requires `D-' and `D+' pins which are defined by protocol to transmitting data.
Without these pins, data can't be transferred via USB cable. Based on this fact, USB Condom \cite{Condom} is a hardware solution to block data channel by adding blocker in the connector. This blocker can cut off the `D-' and `D+' connection while leave power pins intact.
However, this method poses a great challenge to plug-and-play property of USB, as once it is deployed, it will stop all USB functions other than charging.

>>>>

In this part, we surveyed related works on USB attack in Section~\ref{subsec:usb_attack}, and USB defence security in Section \ref{subsec:usb_defence}, respectively.

@@

From the hardware perspective, BadUSB attack requires data lane \mbox{(D+ \& D-)} which are defined by protocol to transmitting data.
Without these pins, data can't be transferred via USB cable. Based on this fact, USB Condom \cite{Condom} is a hardware solution to block data channel by adding blocker in the connector. This blocker can cut off the data lane \mbox{(D+ \& D-)} connection while leave power pins intact.
However, this method poses a great challenge to plug-and-play property of USB, as once it is deployed, it will stop all USB functions other than charging.

### 2021-03-21 WOOT/Files/badusb.tex

\textbf{\ac{HID} Emulation Mode.} This mode mainly relies on the ``\ac{HID} Emulator'' in Figure~\ref{fig:attack_model} to
send constructed \ac{HID} packet to the victim. These constructed \ac{HID} packets are
interpreted by the victim as valid keystrokes and mouse moves. Thus, the
attacker can execute arbitrary scripts on the victim's device. This is the
function of the original BadUSB. Based on this, we made the following
improvements.

First, as \tool has established a feedback channel using \ac{USB} 3.x protocol, when performing keystroke and mouse movement injection, an attacker can obtain real-time feedback from the victim's devices. This feedback allows an attacker to tell whether the previous attack succeeded and decide what to perform next. Existence of such a feedback channel largely strengthens the attack ability of \tool.

@@

When running in this mode, \tool passively processes the victim's video stream
and detects ``valuable'' private data.  The data is considered as
``valuable'' or not by a customized detector. We implemented a simple
payment code detector for the proof-of-concept purpose, which demonstrates that we successfully transfer money from a victim to an
attacker. More detail can be obtained in Section~\ref{sec:experiment}.

>>>>

\textbf{\ac{HID} Emulation Mode.} This mode mainly relies on the ``\ac{HID} Emulator'' in Figure~\ref{fig:attack_model} to
send constructed \ac{HID} packet to the victim. These constructed \ac{HID} packets are
interpreted by the victim as valid keystrokes and mouse movements. Thus, the
attacker can execute arbitrary scripts on the victim's device. This is the
function of the original BadUSB. Based on this, we made the following
improvements.

First, as \tool has established a feedback channel using \ac{USB} 3.x protocol, when performing keystroke and mouse movement injection, an attacker can obtain real-time feedback from the victim's device. This feedback allows an attacker to tell whether the previous attack succeeded and decide what to perform next. Existence of such a feedback channel largely strengthens the attack ability of \tool.

@@

When running in this mode, \tool passively processes the victim's video stream
and detects ``valuable'' private data.  The data is considered as
``valuable'' or not by a customized detector. We implemented a simple
payment code detector for the proof-of-concept purpose, which demonstrates that we successfully transfered money from a victim to an
attacker. More detail can be obtained in Section~\ref{sec:experiment}.

### 2021-03-21 WOOT/Files/introduction.tex

In this work, we addressed the limitations mentioned
above and implemented a multi-mode attack model of \ac{USB}, named \tool.  \tool
extends BadUSB to support the features of \ac{USB} Type-C.  
Although many smartphones equipped with USB-C connectors do not support \ac{USB} 3.x protocol, such as the products of Xiaomi, more and more vendors like HUAWEI and Samsung tend to support \ac{USB} 3.x protocol in their \mbox{high-end} smartphones~\cite{usbclist}.
Since \mbox{\ac{USB} Type-C} can transfer video stream data, \tool could obtain the information of the
victim's \ac{GUI} during attacks.  Combining it with the emulation
of traditional \acp{HID}, e.g., keyboards and mice, attackers are capable of
performing precise attacks.  
%We did experiments to verify that \tool could also
%bypass some countermeasures for BadUSB since they often rely on interaction
%with the graphical interface.

Moreover, we implemented multiple attacking
modes of \ac{USB} attacks based on our approach to verify its effectiveness,
including \ac{HID} Emulator Mode, Video Capture Mode, and Full Control Mode.  To improve the
efficiency and performance of \tool, we designed a filtering algorithm to
preprocess the video data before network transmission.  Moreover, we conducted
a series of experiments for each attack mode as well as for different types of
devices, including smartphones, personal computers, and tablet computers, to
validate the usability of \tool.  We also conducted a user study for attacks in
sharing power banks, one of the application scenarios of \tool.  During the
user study, we obtained a large amount of sensitive data through \tool, since
users are usually unconscious of the necessity to check the \ac{USB} devices they
plugged in for security purposes.  
Ten volunteers participated in the user study.
Finally, we found that 4,796 of 94,058 records obtained by \tool are related to users' privacy information.
After the validation of our attack model, we
proposed several defense methods as countermeasures, including external
hardware authorization, distrust-by-default, etc.  It is worth noting that we
designed a method, called isolated \ac{UI} rendering, to separate the user interface
into sensitive and insensitive layers.  Only the insensitive layer's content will be passed to the insecure driver and thus rendered on the external display, protecting the sensitive layer's content.
%\shuqing{Case study, evaluation, notable results.}

>>>>

In this work, we addressed the limitations mentioned
above and implemented a multi-mode attack model of \ac{USB}, named \tool.  \tool
extends BadUSB to support the features of \ac{USB} Type-C.  
Although many smartphones equipped with USB-C connectors do not support \ac{USB} 3.x protocol, such as some non-flagship products of Xiaomi, more and more vendors like HUAWEI and Samsung tend to support \ac{USB} 3.x protocol in their \mbox{high-end} smartphones~\cite{usbclist}.
Since \mbox{\ac{USB} Type-C} can transfer video stream data, \tool could obtain the information of the
victim's \ac{GUI} during attacks.  Combining it with the emulation
of traditional \acp{HID}, e.g., keyboards and mice, attackers are capable of
performing precise attacks.  
%We did experiments to verify that \tool could also
%bypass some countermeasures for BadUSB since they often rely on interaction
%with the graphical interface.

Moreover, we implemented multiple attacking
modes of \ac{USB} attacks based on our approach to verify its effectiveness,
including \ac{HID} Emulator Mode, Video Capture Mode, and Full Control Mode.  To improve the
efficiency and performance of \tool, we designed a filtering algorithm to
preprocess the video data before network transmission.  Moreover, we conducted
a series of experiments for each attack mode as well as for different types of
devices, including smartphones, personal computers, and tablet computers, to
validate the usability of \tool.  We also conducted a user study for attacks in
sharing power banks, one of the application scenarios of \tool.  During the
user study, we obtained a large amount of sensitive data through \tool, since
users are usually unconscious of the necessity to check the \ac{USB} devices they
plugged in for security purposes.  
After the validation of our attack model, we
proposed several defense methods as countermeasures, including external
hardware authorization, distrust-by-default, etc.  It is worth noting that we
designed a method, called isolated \ac{UI} rendering, to separate the user interface
into sensitive and insensitive layers.  Only the insensitive layer's content will be passed to the insecure driver and thus rendered on the external display, protecting the sensitive layer's content.
%\shuqing{Case study, evaluation, notable results.}
